Model Recognition as Planning

### 2018-05-23 doc/aaai-19/model-recognition.tex
added more notes on model recognition

\section{Model Recognition as Planning}
\label{sec:asPlanning}
Now we show a classical planning compilation for computing the {\em observation edit distance} $\delta(\mathcal{M},\mathcal{T})$ for each $\mathcal{M}\in M$. The compilation follows these assumptions
\begin{enumerate}
\item The initial state $s_0\in\mathcal{T}$ is {\em fully observable}.
\item Intermediate actions $a_i\in\mathcal{T}$ and states $s_i\in\mathcal{T}$ s.t. {\small $1\leq i\leq n$}, can be {\em partially observed}. This means that some fluents in $s_i$ may be missing because its value is unknown. In the extreme, entire states $s_i$ can be missing. 
\item $\mathcal{T}$ is {\em noiseless}, meaning that if a fluent or an action is observed it is the correct value. 
\end{enumerate}

>>>>

\subsection{Getting rational}
The {\em \strips\ probability distribution} assigns the same probabaility value to any hypothesis model $\mathcal{M}\in M$ that can reproduce the given observation $\mathcal{T}$. If the input plan execution $\mathcal{T}$ is partially observed, then it is easier that many different models can reproduce the same observations because the input observation is less constrained. A particular case of interest is when $\mathcal{T}=\tup{s_0, s_n}$ that is, when the given observation is an {\em input-output} example.

If we assume that the observed agent is acting rationally, like in {\em plan recognition as planning}~\cite{ramirez2012plan,ramirez2009plan}, one can go one step further and define a probability distribution that considers how an hypothesis $\mathcal{M}\in M$ reproduces an observation $\mathcal{T}$. Defining as more probable hypothesis that can reproduce observations in less steps for instance, using the expression: $\frac{1}{1+e^{-cost(\pi^*_{\mathcal{M},\mathcal{T}})}}$ where $\pi^*_{\mathcal{M},\mathcal{T}}$ is an optimal plan (according to $\mathcal{M}$) that reproduces $\mathcal{T}$.

\section{Model Recognition as Planning}
\label{sec:asPlanning}
Now we show a classical planning compilation for computing the {\em observation edit distance} $\delta(\mathcal{M},\mathcal{T})$ for each $\mathcal{M}\in M$. The compilation follows these assumptions
\begin{enumerate}
\item The initial state $s_0\in\mathcal{T}$ is {\em fully observable}.
\item Intermediate actions $a_i\in\mathcal{T}$ and states $s_i\in\mathcal{T}$ s.t. {\small $1\leq i\leq n$}, can be {\em partially observed}. This means that some fluents in $s_i$ may be missing because its value is unknown. In the extreme, entire states $s_i$, {\small $1\leq i\leq n$}, can be missing. 
\item $\mathcal{T}$ is {\em noiseless}, meaning that if a fluent or an action is observed it is the correct value. 
\end{enumerate}
